Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
twang

  for (i in 1:n_imputations) {
    emm_probs <- emmeans(models[[i]], 
                         ~ ever_lapse_binary | dr_severity * any_treatment,
                         type = "response",
                         weights = "proportional")
    all_probs[[i]] <- as.data.frame(emm_probs)
  }

@@

  for (j in 1:n_cells) {
    # Extract probabilities for this cell
    probs <- sapply(all_probs, function(x) x$prob[j])
    ses <- sapply(all_probs, function(x) x$SE[j])

>>>>

  for (i in 1:n_imputations) {
    emm_probs <- emmeans(models[[i]], 
                         ~ ever_lapse_binary | dr_severity * any_treatment,
                         type = "response",
                         weights = "proportional")
    df_probs <- as.data.frame(emm_probs)

    # Find the probability column (could be "prob", "response", "emmean", etc.)
    prob_col <- names(df_probs)[grep("prob|response|emmean", names(df_probs), ignore.case = TRUE)[1]]
    se_col <- names(df_probs)[grep("SE|se", names(df_probs))[1]]

    # Standardize column names
    df_probs$prob <- df_probs[[prob_col]]
    df_probs$SE <- df_probs[[se_col]]

    all_probs[[i]] <- df_probs
  }

@@

  for (j in 1:n_cells) {
    # Extract probabilities for this cell - now we know the column exists
    probs <- sapply(all_probs, function(x) x$prob[j])
    ses <- sapply(all_probs, function(x) x$SE[j])
